% \cleardoublepage
% \addcontentsline{toc}{chapter}{\bibname}
\begin{thebibliography}{99}

\bibitem{pfeiffer} 
Pfeiffer Vacuum Technology AG,
\textit{HiCube Eco Turbo pumping stations},
\url{https://www.lesker.com/newweb/vacuum_pumps/pdf/manuals/hicube-eco-operating-manual.pdf}

\bibitem{source_dfa} 
Dipartimento di Fisica e Astronomia ``Galileo Galilei'',
\textit{Sorgenti Radiogene},
\url{https://www.dfa.unipd.it/fileadmin/servtec/Sorgenti_polo_ott_2019_corretto.pdf}

\bibitem{source_ez} 
Eckert \& Ziegler,
\textit{Reference \& Calibration Sources},
\url{https://www.ezag.com/fileadmin/user_upload/isotopes/isotopes/Isotrak/isotrak-pdf/Product_literature/EZIPL/EZIP_catalogue_reference_and_calibration_sources.pdf}

\bibitem{source_ddep} 
Laboratoire National Henri Becquerel,
\textit{Table de Radionucléides, Am-241},
\url{http://www.nucleide.org/DDEP_WG/Nuclides/Am-241_tables.pdf}

\bibitem{ssb_detector} 
AMETEK ORTEC,
\textit{Review of the Physics of Semiconductor Detectors},
\url{http://nuchem.iucf.indiana.edu/SiSpecs/SBD_det_cat.pdf}

\bibitem{canberra_2003BT} 
Canberra Industries Inc,
\textit{Model 2003BT Silicon Surface Barrier Detector Preamplifier},
\url{https://mirion.s3.amazonaws.com/cms4_mirion/files/pdf/spec-sheets/c40680_2003bt_preamp_spec_sheet.pdf?1560277821}

\bibitem{canberra_2024}
Canberra Industries Inc,
\textit{Model 2024 Fast Spectroscopy Amplifier},
\url{http://ohm.bu.edu/~pbohn/REPAIR__Advanced_Lab/Mossbauer/Data_Sheets/Model_2024_Super_Spec.pdf}

\bibitem{picoscope_5000}
Pico Technology Limited,
\textit{PicoScope 5000 Series},
\url{https://www.picotech.com/download/datasheets/PicoScope5000Series.pdf}

\bibitem{Suljic} 
Miljienko \v{S}ulji\'c.
\textit{Study of Monolithic Active Pixel Sensors for the Upgrade of the ALICE Inner Tracking System}. 
Università degli studi di Trieste.
A.A. 2016-2017.

\bibitem{Manual_ALP} 
ALICE ITS ALPIDE development team.
\textit{ALPIDE Operations Manual}.
Ver. 0.3, July 2016

\bibitem{Artix} 
Xilinx.
\textit{7 Series FPGAs Data Sheet: Overview}.
DS180 (v2.6.1) September 8, 2020

\bibitem{Arty_A7}
ARTY A7 board Documentation,
\url{https://reference.digilentinc.com/reference/programmable-logic/arty-a7/reference-manual}

\bibitem{tesi_gabri} 
Gabriele Bortolato.
\textit{Sviluppo del firmware per il controllo del detector ALPIDE ed implementazione su FPGA}.
Università degli studi di Padova.
A.A. 2019-2020.

\bibitem{IPBus}
IPBus Documentation, \url{https://ipbus.web.cern.ch/ipbus/}

\bibitem{DE0}
DE0-nano Cyclone IV Documentation, \url{http://www.terasic.com.tw/cgi-bin/page/archive.pl?Language=English&No=593&PartNo=4}

\bibitem{alphaMC}
AlfaMC: a fast alpha particle transport Monte Carlo code, \url{https://arxiv.org/pdf/1211.5960.pdf}

\end{thebibliography}
